Blum axioms and nondeterministic computation of functions

### 2016-04-19 paper.tex
paper.tex: Mention FNP-completeness.

>>>>

\subsubsection{Extension $\NP$-completeness}

The last definition provides an extension of the class $\NP$ to function computation,
so the next step is extend the concept of $\NP$-completeness.

Call $\FNP$ the class of all functions computable in polynomial time,
under our definition.
A language $L$ is $\NP$-complete if both $L \in \NP$
and every language in $\NP$ reduces to $L$;
that is, for every language $L' \in \NP$,
there is a polynomial-time computable function $f$
such that, for every $x$,
\begin{equation*}
    x \in L' \text{ if and only if } f(x) \in L.
\end{equation*}
(We are using Karp reductions here \cite[p.~42]{AroraBarak2009}.)
If we rephrase in terms of the characteristic functions $1_L$ and $1_{L'}$,
of $L$ and $L'$, respectively,
we have $1_{L'}(x) = 1_L(f(x))$ for all $x$.
We will generalize specifically this equation to define $\FNP$-completeness.

\begin{definition}
    A function $f$ is $\FNP$-complete if $f \in \FNP$ and,
    for every function $g$ in $\FNP$,
    there is a polynomial-time computable function $h$ such that
    \begin{equation*}
        g(x) = f(h(x))
    \end{equation*}
    for every $x \in \{0, 1\}^*$.
\end{definition}

We can construct a $\FNP$-complete function based on the halting problem:
define $f : \{0, 1\}^* \times \mathbb N \to \{0, 1\}^*$
such that $f(w, n)$ is the lexicographically greatest value written by any branch of $w$
after running for $n$ steps.
Such functions are $\FNP$-complete
because they simulate Turing machines directly.

However, this definition is very rigid
and allow for few functions to be $\FNP$-complete.
For example, if $g$ is a function that returns
(say) a largest clique in a graph,
any candidate function for $\FNP$-completeness
must be able to output representation of graphs.
This restrict the class of $\FNP$-complete functions
to functions like the one mentioned above.
